### 2023-09-11 README.Rmd
adding table with links

- Paper [PDF](documents/paper/paper.pdf)
- Supplementary Materials [PDF](documents/supplementary/supplementary.pdf)

>>>>

|               |                                                  |                                                  |
|---------------|--------------------------------------------------|--------------------------------------------------|
| **Paper**         | [pdf](documents/paper/paper.pdf)                 | [rmd](documents/paper/paper.Rmd)                 |
| **Supplementary** | [pdf](documents/supplementary/supplementary.pdf) | [rmd](documents/supplementary/supplementary.Rmd) |
